### 2022-02-02 README.Rmd
Remove Binder link
Address reviewer feedback

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/FlukeAndFeather/cetaceanbcg/main?urlpath=rstudio)

@@

## How to run in your broswer or download and run locally

>>>>

[![DOI](https://zenodo.org/badge/399999855.svg)](https://zenodo.org/badge/latestdoi/399999855)

@@

## How to download and run locally
